Copy number variants in rheumatoid arthritis data from inferCNV

### 2024-02-07 infercnv/reports/infercnv.Rmd
change knit infercnv back to manual integration of all pngs

---
title: "Copy number variants in rheumatoid arthritis data from inferCNV"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: true
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
    rerun: true
---

@@

# chunk options
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE)

@@

```{r, results = 'asis'}
pngs <-
  list.files(pattern = '^BRI', include.dirs = T) %>%
  purrr::set_names() %>%
  purrr::map(function(id) {
    lis <-
      list.files(id, pattern = '.png', recursive = T, full.names = T) %>%
      {setNames(., gsub('infercnv.', '', tools::file_path_sans_ext(basename(.))))}

>>>>

---
title: "Copy number variants in rheumatoid arthritis data from inferCNV"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: false
    code_folding: hide
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
  infercnv_dir: NULL
  rerun: true
---

@@

# chunk options
knitr::opts_knit$set(root.dir = '../')
knitr::opts_chunk$set(
  warning = FALSE, 
  dpi = 300, 
  message = FALSE)

@@

```{r, results = 'asis'}
pngs <-
  list.files(params$infercnv_dir,
             pattern = '^BRI', 
             include.dirs = T) %>%
  purrr::set_names() %>%
  purrr::map(function(id) {
    # collect pngs
    lis <-
      list.files(file.path(params$infercnv_dir, id), 
                 pattern = '.png', 
                 recursive = T, 
                 full.names = T) %>%
      {setNames(., gsub('infercnv.', '', tools::file_path_sans_ext(basename(.))))}
